Observed vs. Simulated Year Comparison

### 2023-07-06 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Whoops: squash with previous

```{r obs-error-table-prep}
# rename parameters to human-readable format
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")

@@

# correct origin indices
obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1

@@

# add a type column
obs_error_ests$type = NA
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]

# add levels to each variable
obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))

>>>>

```{r obs-error-table-prep}
# rename parameters to human-readable format
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")

@@

# correct origin indices
obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1

@@

# add a type column
obs_error_ests$type = NA
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]

# add levels to each variable
obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
